Supplementary materials

### 2019-11-05 manuscript/supplemental.Rmd
added cellct

```{r, include=F}
map <- knitr::include_graphics(here::here("manuscript/figs/map.png"))
field <- read_csv(here::here("data/02_tidied/tidied_field.csv"))
field_photos <- knitr::include_graphics(here::here("manuscript/figs/S3_site_field_photos/field_collage.png"))
micro_photos <- knitr::include_graphics(here::here("manuscript/figs/S4_site_micro_photos/micro.png"))
s18 <- include_graphics(here("manuscript/figs/18s_algae_rel_abund.png"))
tree <- include_graphics(here("manuscript/figs/otu_tree.png"))
tree_taxonomy <- include_graphics(here("manuscript/figs/taxonomy_tree.png"))
diversity <- include_graphics(here("manuscript/figs/diversity.png"))
cellct <- include_graphics(here("manuscript/figs/supp/cellct/cellct.png"))

map_cap <- "S1. Map showing locations of snow algae sampling locations in summer 2018."
table_cap <- "S2. Table of sample site information of sequenced snow algae samples."
field_photo_cap <- "S3. Photos of snow algae field sites."
micro_cap <- "Microphotos of snow algae samples included in sequencing run."
s18_cap <- "Relative abundance barplot of 18S amplicon library"
tree_cap <- "Maximum likelihood tree of rbcL amplicon library. Colors represent OTU assignments."
tax_tree_cap <- "Maximum likelihood tree of rbcL amplicon library. Colors represent taxonomic assignments."
diversity_cap <- "A. Shannon diversity of snow algae samples, plotted against sample elevation. Smooth method = linear model. B. Faith's phylogenetic diversity plotted against sample elevation."
(ref:cellct_cap) "Heatmap showing cell count relative abundance from 117 snow algae samples. Cb = Chlainomonas cf. brevispina, Ck=Chloromonas krienitzii, Cn=Chloromonas cf. nivalis, Cr=Chlainomonas rubra, G=green cells, O=other, Sn=Sanguina nivaloides"
```

>>>>

```{r, include=F}
map <- knitr::include_graphics(here::here("manuscript/figs/map.png"))
field <- read_csv(here::here("data/02_tidied/tidied_field.csv"))
field_photos <- knitr::include_graphics(here::here("manuscript/figs/S3_site_field_photos/field_collage.png"))
micro_photos <- knitr::include_graphics(here::here("manuscript/figs/S4_site_micro_photos/micro.png"))
cellct <- include_graphics(here("manuscript/figs/supp/cellct/cellct.png"))
s18 <- include_graphics(here("manuscript/figs/18s_algae_rel_abund.png"))
tree <- include_graphics(here("manuscript/figs/otu_tree.png"))
tree_taxonomy <- include_graphics(here("manuscript/figs/taxonomy_tree.png"))
diversity <- include_graphics(here("manuscript/figs/diversity.png"))

map_cap <- "S1. Map showing locations of snow algae sampling locations in summer 2018."
table_cap <- "S2. Table of sample site information of sequenced snow algae samples."
field_photo_cap <- "S3. Photos of snow algae field sites."
micro_cap <- "Microphotos of snow algae samples included in sequencing run."
cellct_cap <- "Heatmap showing cell count relative abundance from 117 snow algae samples. Cb = \\emph{Chlainomonas cf. brevispina}, Ck=\\emph{Chloromonas krienitzii}, Cn=\\emph{Chloromonas cf. nivalis}, Cr=\\emph{Chlainomonas rubra}, G=green cells, O=other, Sn=\\emph{Sanguina nivaloides}"
s18_cap <- "Relative abundance barplot of 18S amplicon library"
tree_cap <- "Maximum likelihood tree of rbcL amplicon library. Colors represent OTU assignments."
tax_tree_cap <- "Maximum likelihood tree of rbcL amplicon library. Colors represent taxonomic assignments."
diversity_cap <- "A. Shannon diversity of snow algae samples, plotted against sample elevation. Smooth method = linear model. B. Faith's phylogenetic diversity plotted against sample elevation."

```
